Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-25 2016-Weak-FH-Bisim/WeakBisim.tex
notation + ajout refs

\subsection{Running Example}
\TODO{Rabea: trouver reference !!}
To illustrate this work, we use a simple transport protocol, that provides safe transport of data between two processes,
over unsafe media.

@@

 \noindent                        
 \begin{small} $\Pred_{s,t} \land \Pred_{OT}\\ 
 \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
 	%reversed 
 	%substitution 
 	\implies  \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 	\Pred_{OT_x}
 	\land \alpha_Q\!=\!\alpha_x \land  
 	\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
 }
 \\~\qquad\quad \Pred\,'\land\alpha_Q=\beta_{j_0} \\
 	\implies
 	 \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 		\Pred\,'\land \Pred_{OT_x}
 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
 	~\qquad\quad 	\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
 	 $\end{small}

 Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
 implication hypothesis.
 %\TODO{There was a confusion between the $\Rightarrow$ between the
 %  steps, and the $\implies$ inside the formulas...}
% 
% Explanations: first, we reversed the substitution; then we
% restricted the 
% substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
% applied the property of FH-bisimulation for $P$ and rearranged the
% terms using the fact that $v_Q=v_x$.
 The obtained formula reaches the goal except for 
 two points:\\[-4.3ex] 
 \begin{itemize}
 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
 	adding prerequisite on more variables 
 	does not   	change the validity of the formula (those variables are not used).
 	\item Concerning the last term, we need 
 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
 	$\Pred_{s x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
 	and thus the substitution $\subst{Post\,'}$ has no effect on it.
 \end{itemize}	
Finally: \\
\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies\\
{\displaystyle\bigvee_{x\in X}
 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
 		\big(\Pred\,'\land\! \Pred_{OT_x}
 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
 		}$
 		\end{small}\\
This proves the  condition of the FH-simulation, the other direction is 
 similar.\qed

@@

\noindent                        
\begin{small} 
$\Pred_{s,t} \land \Pred_{OT}\\ \implies
 \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
 \implies  \hspace{-2ex}
{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
\!\land \!
\Pred_{OT_x}\!\land\! \alpha_Q\!=\!\beta_{j_0}
\land\! \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
\land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
\Pred\,''\\ % 
			%FH for P
 \implies  \hspace{-2ex}
	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
\land \!
\left(\Pred_{OT_x}\!\land\!
\Pred\,''\!
\land \alpha_Q\!=\!\beta_{j_0 x}\right)
\land \alpha\!=\!\alpha_x}} 
\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
$\end{small}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_j^1}}\\
s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
$

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\Rightarrow \,
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
$

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$ 
s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',
\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
$

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred_{s,t} \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \!\land\!  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$

@@

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {t \OTWeakarrow {\alpha_{1 a}} u_a}
\end{mathpar}
 such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
     \land\! \alpha_{1 a}\!=\!\tau \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

@@

\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
\end{mathpar}
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_a} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
 \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$

\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\end{mathpar}
 such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
 $\Pred_{s_{21},v_{b}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
     \land\!  
     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$

@@

$\Pred_{s,t} \land \Pred\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 

@@

$\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a} \land
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}

@@

    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\land \\~\qquad\qquad\alpha'\!=\!\alpha_{2 b}\! \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 

>>>>

\subsection{Running Example}
\TODO{Rabea: trouver reference !!}
To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media. The alternating bit protocol was first described in \cite{Bartlett:1969}.  Our specification  of the ABP is based on the one given in \cite{Vergamini:1986}.

@@

 \noindent                        
 \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
 \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
 	%reversed 
 	%substitution 
 	\implies  \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 	\Pred_{OT_x}
 	\land \alpha_Q\!=\!\alpha_x \land  
 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
 }
 \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
 	\implies
 	 \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 		\Pred\,'\land \Pred_{OT_x}
 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
 	 $\end{small}

 Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
 implication hypothesis.
 %\TODO{There was a confusion between the $\Rightarrow$ between the
 %  steps, and the $\implies$ inside the formulas...}
% 
% Explanations: first, we reversed the substitution; then we
% restricted the 
% substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
% applied the property of FH-bisimulation for $P$ and rearranged the
% terms using the fact that $v_Q=v_x$.
 The obtained formula reaches the goal except for 
 two points:\\[-4.3ex] 
 \begin{itemize}
 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
 	adding prerequisite on more variables 
 	does not   	change the validity of the formula (those variables are not used).
 	\item Concerning the last term, we need 
 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
 	$\Pred_{s x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
 	can conclude by observing that	$\Pred_{s,x}$ does not use any variable of $P$ 
 	and thus the substitution $\subst{Post\,'}$ has no effect on it.
 \end{itemize}	
Finally: \\
\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies\\
{\displaystyle\bigvee_{x\in X}
 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
 		\big(\Pred\,'\land\! \Pred_{OT_x}
 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
 		}$
 		\end{small}\\
This proves the  condition of the FH-simulation, the other direction is 
 similar.\qed

@@

\noindent                        
\begin{small} 
$\Pred_{s,t} \land \Pred_{OT} \implies
 \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
 \implies  \hspace{-2ex}
{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
\!\land \!
\Pred_{OT_x}\!\land\! \alpha_Q\!=\!\beta_{j_0}
\land\! \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
\land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
\Pred\,''\\ % 
			%FH for P
 \implies  \hspace{-2ex}
	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
\land \!
\left(\Pred_{OT_x}\!\land\!
\Pred\,''\!
\land \alpha_Q\!=\!\beta_{j_0 x}\right)
\land \alpha\!=\!\alpha_x}} 
\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
$\end{small}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
$

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\Rightarrow \,
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
$

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$ 
s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',\quad
\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ),\quad \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
$

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred_{s,t} \land \Pred_{OT}\implies\\
\displaystyle{\bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \!\land\!  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$

@@

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {t \OTWeakarrow {\alpha_{1 a}} u_a}
\end{mathpar}
 such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\implies\\
 \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
     \land\! \alpha_{1 a}\!=\!\tau \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

@@

\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
\end{mathpar}
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_a} \land \Pred_2\implies\\
\displaystyle{\bigvee_{b\in B}}
 \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$

\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\end{mathpar}
 such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
 $\Pred_{s_{21},v_{b}} \land \Pred_3\implies\\
\displaystyle{\bigvee_{c\in C}}
   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
     \land\!  
     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$

@@

$\Pred_{s,t} \land \Pred\implies\\
 \displaystyle{\bigvee_{x\in X}} 

@@

$\Pred_{s,t} \land \Pred_1\implies\\
 \displaystyle{\bigvee_{a\in A}}

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
 \displaystyle{\bigvee_{a\in A}}
  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
\displaystyle{\bigvee_{a\in A}}

@@

    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\

@@

$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}. (\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 
